\documentclass[a4paper,12]{article}

\usepackage{listings}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{a4wide}
\usepackage{tikz}
\usetikzlibrary{shapes, calc, shapes, arrows}
\usepackage{relsize}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{algorithm2e}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pxfonts}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{abstract}

\lstset{basicstyle=\ttfamily,
literate=
  {á}{{\'a}}1 {é}{{\'e}}1 {í}{{\'i}}1 {ó}{{\'o}}1 {ú}{{\'u}}1
  {Á}{{\'A}}1 {É}{{\'E}}1 {Í}{{\'I}}1 {Ó}{{\'O}}1 {Ú}{{\'U}}1
  {à}{{\`a}}1 {è}{{\`e}}1 {ì}{{\`i}}1 {ò}{{\`o}}1 {ù}{{\`u}}1
  {À}{{\`A}}1 {È}{{\'E}}1 {Ì}{{\`I}}1 {Ò}{{\`O}}1 {Ù}{{\`U}}1
  {ä}{{\"a}}1 {ë}{{\"e}}1 {ï}{{\"i}}1 {ö}{{\"o}}1 {ü}{{\"u}}1
  {Ä}{{\"A}}1 {Ë}{{\"E}}1 {Ï}{{\"I}}1 {Ö}{{\"O}}1 {Ü}{{\"U}}1
  {â}{{\^a}}1 {ê}{{\^e}}1 {î}{{\^i}}1 {ô}{{\^o}}1 {û}{{\^u}}1
  {Â}{{\^A}}1 {Ê}{{\^E}}1 {Î}{{\^I}}1 {Ô}{{\^O}}1 {Û}{{\^U}}1
  {œ}{{\oe}}1 {Œ}{{\OE}}1 {æ}{{\ae}}1 {Æ}{{\AE}}1 {ß}{{\ss}}1
  {ű}{{\H{u}}}1 {Ű}{{\H{U}}}1 {ő}{{\H{o}}}1 {Ő}{{\H{O}}}1
  {ç}{{\c c}}1 {Ç}{{\c C}}1 {ø}{{\o}}1 {å}{{\r a}}1 {Å}{{\r A}}1
  {€}{{\euro}}1 {£}{{\pounds}}1 {«}{{\guillemotleft}}1
  {»}{{\guillemotright}}1 {ñ}{{\~n}}1 {Ñ}{{\~N}}1 {¿}{{?`}}1
}

% Disable text indent for paragraph
\setlength{\parindent}{0pt}

\title{Artificual Neural Networks \& Deep QLearning}
\author{Jan Vincent Hoffbauer\\
jan.hoffbauer@rwth-aachen.de }
\date{\today}

\begin{document}

\maketitle
~\\
\\
\\

\begin{abstract}
In this paper I describe Artificial Neural Networks and Deep Q-Learning. I briefly sumarize the mathematical background and present usage examples of these algorithms. Furthermore I apply them to practical examples. 
\end{abstract}
  
\newpage
\tableofcontents
\newpage

% List all citations
\nocite{*}

% Introduction
\section{Introduction}
Machine learning has become an important of computer science. Since the development of the internet, huge amounts of data are becoming available. The machine learning algorithms presented in this paper can derive knowledge from such data. For example, artificial neural networks can be used to recognize faces on images or predict trends in the stock market. 
\\
\\
In this paper I will first introduce, how machine learning models can be evaluated. Then I will introduce artificial neural networks and Deep Q-Learning, to give the reader a basic overview about different machine learning technologies. 


\input{topics/evaluate_models}
\input{topics/ann}
\input{topics/dqn}


\section{Conclusion and Outlook}
I presented two machine learning models and showed, how they can be used in practice. In this paper I showed only basic machine learning models. These models can be extended to more complex and more powerfull models. For example artificial neural networks are not limited to the basic feedforward multilayer structure. They can be extended to convolutional neural networks, which are very good at image processing. The presented Deep Q-Learning algorithm can be extended to Double Deep Q-Learning. This algorithm has better convergence properties. 
\\
\\
In general I think, that machine learning is a topic, which is very important for computer science. Due to the huge amounts of data becoming available and the advancing research into this topic, I expect this topic to develop rapidly.


\newpage
\bibliography{paper} 
\bibliographystyle{ieeetr}

\end{document}
